\LARGE{{\bf{Gravitational Wave Signals from Multiple Hidden Sectors} \\ }}

### 2019-10-24 gwnnDraft02.tex
specified spectral shape around peak frequencies

Shifting to the other part of our framework, our results leads to the question ``how well can experiments probe non power law signals?" For frequency ranges away from the peak of the total, GW signals the quoted detection thresholds should hold: the signals fall off as a power law to a very good approximation. However, for areas around the peak frequency the answer is less clear; the PLI curves are built under the assumption of a power law. Work has been done \cite{alanne2019fresh} in examining GW signals using peak amplitudes and peak frequencies as the defining observables: this is rooted in the assumption that GW signals have a model-independent spectral shape. However, our results indicate that this assumption of model-independence cannot hold for all cases: sectors with similar (but different) transition temperatures can create either peak broadening or multi-hump features that differ significantly from a standard power law shape.  This points to the need for future work to better understand where the power law approximation breaks down and how this affects detection prospects for the next generation of GW detectors.

>>>>

Shifting to the other part of our framework, our results leads to the question ``how well can experiments probe non power law signals?" For frequency ranges away from the peak of the total, GW signals the quoted detection thresholds should hold: the signals fall off as a power law to a very good approximation. However, for areas around the peak frequency the answer is less clear; the PLI curves are built under the assumption of a power law. Work has been done \cite{alanne2019fresh} in examining GW signals using peak amplitudes and peak frequencies as the defining observables: this is rooted in the assumption that GW signals have a model-independent spectral shape around peak frequencies. However, our results indicate that this assumption of model-independence cannot hold for all cases: sectors with similar (but different) transition temperatures can create either peak broadening or multi-hump features that differ significantly from a standard power law shape.  This points to the need for future work to better understand where the power law approximation breaks down and how this affects detection prospects for the next generation of GW detectors.
